Missing links and the topological robustness of food webs

### 2023-06-26 manuscript/ms_C3_v3.Rmd
Update ms_C3_v3.Rmd

 1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs. Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links. Simultaneously, models might predict links which cannot occur, i.e., real false positives. 
  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than the observed ones. Thus, we expect that predicted food webs are more robust than the observed ones. However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e. the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links. We did this for 12 different food webs from a wide variety of ecosystems. We used three extinction scenarios: random, most connected, and least connected.
  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs. On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios. On the other hand, we saw no effect or very little effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
  5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models. Also, the differences in the structural properties of the model predicted food webs and the observed food webs suggest structural properties of a food web could be used as summary statistics to fit models such as the ADBM to the observed data.

@@

Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity and can lead to food web collapse [@ullah2018]. This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species due to environmental change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004]. An example of a secondary extinction is when a consumer goes extinct because its sole resource species goes extinct. Therefore, research focused on cascading secondary extinctions, also known as 'community viability analysis', has been performed extensively in the past few decades to quantify how robust food webs are to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005]. This research revealed that the rate of collapse of a food web depends on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].

Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009]. Primary species loss is considered to be extinction of a species due to causes external to the food web, e.g. overharvesting [@koningGrassrootsReservesRescue2021], introduction of invasive species [@davidImpactsInvasiveSpecies2017]. A secondary extinction is an extinction caused by a previous extinction (either primary or secondary). Numerous studies have used topological criterion for assigning a secondary extinction to a species, i.e., if extinction is of the last resource species of a consumer species, then the consumer species suffers secondary extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @soleComplexityFragilityEcological2001].

@@

A key assumption of the observed food webs is that they are very well sampled, i.e. all the links that in reality can occur are represented. However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016]. Some rare trophic links require more sampling effort than others, whereas some trophic links (sometimes referred to as forbidden links) remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016]. Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones. One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008; @gupta2023many] to predict the missing links and then measure the robustness of the predicted food web. The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare. However, this solution is not infallible, as it is likely that the food web model might still miss some links and also may predict some links that could not, in fact occur.

@@

In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs. We achieved this by simulating primary species loss in 12 food webs predicted by the model to quantify secondary loss of extinctions and compare the robustness of food webs predicted by the model to the robustness of the observed food webs. We expect the model predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the model predicts greater connectance compared to that of the observed food webs. We also examined how different structural food web properties other than the connectance can influence this difference in the perceived robustness. In order to do that, we define our null hypothesis to be: (H1) The missing links that are filled in by the model increase robustness because they increase connectance; and our alternate hypothesis to be: (H2) Although the model fills in missing links, it also changes other structural properties and these outweigh the effects of connectance on robustness.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966]. We chose this model because it is known to predict greater connectance in the predicted food webs compared to the observed food webs [@guptaSimultaneouslyEstimatingFood2022]. The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008]. The foraging variables used in the model are the energy content of prey, handling times of the predator on prey, space clearance rate, i.e. how fast a predator searches space, and prey densities. Each of these variables is derived from the allometric scaling relationship using the body sizes of species. More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in open access @petchey2008.

@@

Given a primary removal of species in a food web, if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web, and a secondary extinction was recorded. Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded. Once no more secondary extinctions occurred, then another primary extinction was made of the next appropriate species depending on the extinction scenario. This process was carried out until all the species were extinct from the food web.

@@

In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web to random extinction. To quantify the effect of undersampling, i.e. greater connectance of connectance, we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (i.e. 0.5 for $R_{50}$ and 1 for connectance). However, we did not perform any statistical significance test because we work with simulated food webs and therefore, the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].

@@

The model food webs were more robust than the observed food webs on average in the most connected and random extinction scenarios (Fig. \ref{fig:fig_r4} (a, b)). However, there were large variations in the robustness within the model food webs in the most connected extinction scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs for the Caricaie Lakes food web was more robust than the observed food web on average but had a larger variation in the robustness within the model food webs compared to other food webs.

The food webs were more robust to the random extinction scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs (Fig. \ref{fig:fig_r4} (b)). Although there were few less robust model food webs in the Broadstone Stream (size aggregation) as shown by the outliers.

In the least connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The model food webs for Small Reef and Benguela Pelagic had very low median robustness. The model food webs for the Benguela Pelagic, Broom and Capinteria food webs had larger variations in robustness when compared to that of the others.

@@

In all of the food webs except Broadstone Stream (taxonomic aggregation) and Skipwith Pond, the effect size of connectance on robustness was positive on average in the most connected extinction scenario (Fig. \ref{fig:fig_r5} (a)), i.e. greater connectance had a positive effect on the robustness. In the random extinction scenario, there was a positive effect of greater connectance on the robustness for Ythan, Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied across the food webs. In the least connected extinction scenario, the median effect sizes were zero for all the food webs except for Caricaie Lakes and Capinteria food webs where the effect sizes were very close to zero and for Benguela Pelagic and Small Reef food webs where the median effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there were lots of outlier with effect sizes negative.

@@

As expected, the model food webs were more robust than the observed food webs on average. The considerable variation of the robustness of the model food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling. Furthermore, as was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average. Future development would be to understand how undersampling, i.e. predicted greater connectance, influences the stability of the dynamics of the model food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria. However, one would expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].

@@

As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM. Real false positive means that the food web model predicts a link between two species that can never interact (The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough. In this case, further sampling should result in the link being observed and a change from false positive to true positive.). Firstly, this may be because the ADBM uses only body size as a trait. A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022]. Secondly, the ADBM can only predict diets that are contiguous with respect to the size of the prey. I.e. it cannot predict that the consumer will consume prey of size 1 and 3, and not consume prey of size 2. However, it is important to note that observed diets are not always contiguous when prey are ordered by their size due to some ecological differences in how predator species choose their prey [@caronAddressingEltonianShortfall]. Hence, it would be intriguing to extend our study to use other food web models based on size-based rules, such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021, to understand if the results are dependent on the decision of model selection. We expect to get a similar result in a size-based deterministic model but a different result, i.e. lower robustness in a size-based stochastic model as compared to the ADBM because the latter can take into account non-contiguity in predator diets [@williamsProbabilisticNicheModel2010]. It would also be interesting to use food web models not based on body size, such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008. We expect to have a difference in results based on whether the trophic interactions in the food webs are governed by size-structured rules or not.

It would be intriguing to know if this difference in connectance has a similar influence on the dynamical stability of the food webs as well. Hence, a prospect could be to use a dynamical model (for example, the bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs. We expect that the greater connectance will lead to reduced dynamical stability in the ADBM predicted food web compared to that of the predicted food web. The difference in stability will be linearly related to the difference in connectance because @martinezDiversityComplexityPersistence has shown that food web stability linearly decreases with connectance.

@@

We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links, i.e. greater connectance on the topological robustness of 12 food webs from various ecosystems. We found that the greater connectance can have a large impact on the robustness of the food webs while at the same time producing large variations in robustness among the predicted food webs. Furthermore, differences in other structural food web properties between the ADBM predicted food webs and the observed food webs are also responsible.

>>>>

 1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs. Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links. Simultaneously, models might predict links which cannot occur, i.e., real false positives. 
  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than the observed ones. Thus, we expect that predicted food webs with fewer missing links are more robust than the observed ones. However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e. the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links. We did this for 12 different food webs from a wide variety of ecosystems. We used three extinction scenarios: random, most connected first, and least connected first.
  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs. On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios. On the other hand, we saw no effect or very little effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
  5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models. Moreover, differences in the structural properties of the model predicted food webs, such as proportion of basal species and maximum trophich height can have large effects on robustness and therefore could be used to further constrain predicted food webs and perhaps produce more constrained predictions of food web robustness.

@@

Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity and can lead to food web collapse [@ullah2018]. This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species due to environmental change and anthropogenic impacts [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004]. An example of a secondary extinction is when a consumer goes extinct because its sole resource species goes extinct. Therefore, research about cascades of secondary extinctions, also known as 'community viability analysis', has been performed extensively in the past few decades to quantify how robust food webs are to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005]. This research revealed that the rate of collapse of a food web depends on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].

Simulation of the effects of primary species loss has been conducted in observed food webs and in model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009]. Primary species loss is considered to be extinction of a species due to causes external to the food web, e.g. overharvesting [@koningGrassrootsReservesRescue2021], introduction of invasive species [@davidImpactsInvasiveSpecies2017]. A secondary extinction is an extinction caused by a previous extinction (either primary or secondary). Numerous studies have used topological criterion for assigning a secondary extinction to a species, i.e., if extinction is of the last resource species of a consumer species, then the consumer species suffers secondary extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @soleComplexityFragilityEcological2001].

@@

A key assumption of the observed food webs is that they are very well sampled, i.e. all the links that in reality can occur are represented. However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016]. Some rare trophic links require more sampling effort than others, whereas some trophic links (sometimes referred to as forbidden links) remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016]. Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones. One solution to compensate for undersampling is, therefore, to  use a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008; @gupta2023many] to predict the missing links and then measure the robustness of the predicted food web. The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare. However, this solution is not infallible, as it is likely that the food web model might still miss some links and also may predict some links that could not, in fact occur.

@@

In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs. We achieved this by simulating primary species loss in 12 food webs predicted by the model to quantify secondary loss of extinctions and comparing the robustness of food webs predicted by the model to the robustness of the observed food webs. We expect the model predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the model predicts greater connectance compared to that of the observed food webs. We also examined how structural food web properties other than the connectance can influence this difference in the perceived robustness. In order to do that, we define our null hypothesis to be: (H1) The missing links that are filled in by the model increase robustness because they increase connectance; and our alternate hypothesis to be: (H2) Although the model fills in missing links, it also changes other structural properties and these outweigh the effects of connectance on robustness.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966]. We chose this model because it is known to predict greater connectance in the predicted food webs compared to the observed food webs [@guptaSimultaneouslyEstimatingFood2022]. The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008]. The foraging variables used in the model are the energy content of prey, handling times of the predator on prey, space clearance rate, i.e. how fast a predator searches space, and prey densities. Each of these variables is derived from the allometric scaling relationship using the body sizes of species. More details on the foraging rules defined in the ADBM and it's predictive power across different food webs can be found in open access @petchey2008.

@@

Given a primary removal of species in a food web, if any remaining species no longer have any resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web, and a secondary extinction was recorded. Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded. Once no more secondary extinctions occurred, then another primary extinction was made of the next appropriate species depending on the extinction scenario. This process was carried out until all the species were extinct from the food web.

@@

In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web to random extinction. To quantify the effect of undersampling, we computed the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance. Normalisation was performed by dividing the variables by their maximum possible values (i.e. 0.5 for $R_{50}$ and 1 for connectance). However, we did not perform any statistical significance test because we work with simulated food webs and therefore, the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].

@@

The model food webs were more robust than the observed food webs on average in the most connected and random extinction scenarios (Fig. \ref{fig:fig_r4} (a, b)). However, there were large variations in the robustness within the model food webs in the most connected extinction scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs for the Caricaie Lakes food web were more robust than the observed food web on average but had a larger variation in the robustness within the model food webs compared to other food webs.

The food webs were more robust to the random extinction scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs (Fig. \ref{fig:fig_r4} (b)).

In the least connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig. \ref{fig:fig_r4} (c)). However there were some exceptions. The model food webs for Small Reef and Benguela Pelagic had very low median robustness. The model food webs for the Benguela Pelagic, Broom and Capinteria food webs had larger variations in robustness when compared to that of the others.

@@

In all of the food webs except Broadstone Stream (taxonomic aggregation) and Skipwith Pond, the effect size of connectance on robustness was positive on average in the most connected extinction scenario (Fig. \ref{fig:fig_r5} (a)), i.e. greater connectance had a positive effect on the robustness. In the random extinction scenario, there was a positive effect of greater connectance on the robustness for Ythan, Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied across the food webs. In the least connected extinction scenario, the median effect sizes were zero for all the food webs except for Caricaie Lakes and Capinteria food webs where the effect sizes were very close to zero and for Benguela Pelagic and Small Reef food webs where the median effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there were many outliers with effect sizes negative.

@@

As expected, the model food webs were more robust than the observed food webs on average. The considerable variation of the robustness of the model food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling. Furthermore, as was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average. Future development would be to understand how undersampling, i.e. predicted greater connectance, influences the stability of the dynamics of the model food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria. One would at least expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].

@@

As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM. Real false positive means that the food web model predicts a link between two species that can never interact. (The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough. In this case, further sampling should result in the link being observed and a change from false positive to true positive.). Firstly, this may be because the ADBM uses only body size as a trait. A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022]. Secondly, the ADBM can only predict diets that are contiguous with respect to the size of the prey. I.e., it cannot predict that the consumer will consume prey of size 1 and 3, and not consume prey of size 2. However, it is important to note that observed diets are not always contiguous when prey are ordered by their size due to some ecological differences in how predator species choose their prey [@caronAddressingEltonianShortfall]. Hence, it would be intriguing to extend our study to use other food web models based on size-based rules, such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021, to understand if the results are dependent on the decision of model selection. We expect to get a similar result in a size-based deterministic model but a different result, i.e., lower robustness in a size-based stochastic model as compared to the ADBM because the latter can take into account non-contiguity in predator diets [@williamsProbabilisticNicheModel2010]. It would also be interesting to use food web models not based on body size, such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008. We expect to have a difference in results based on whether the trophic interactions in the food webs are governed by size-structured rules or not.

It would be intriguing to know if the difference in connectance has a similar influence on the dynamical stability of the food webs as well. Hence, a prospect could be to use a dynamical model (for example, the bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs. We expect that the greater connectance will lead to reduced dynamical stability in the ADBM predicted food web compared to that of the predicted food web. The difference in stability will be linearly related to the difference in connectance because @martinezDiversityComplexityPersistence has shown that food web stability linearly decreases with connectance.

@@

We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links, i.e., greater connectance on the topological robustness of 12 food webs from various ecosystems. We found that the greater connectance can have a large impact on the robustness of the food webs while at the same time producing large variations in robustness among the predicted food webs. Furthermore, differences in other structural food web properties between the ADBM predicted food webs and the observed food webs are also responsible.
